---
pagetitle: "COVID19: Latest numbers and analysis"
output:
  html_document:
    toc: false
    self_contained: false
    lightbox: false
    includes:
       in_header: ./header.html
---

  

```{r setup, include=FALSE, echo=FALSE}
# Technical stuff for webpage
# Create header.html
CON <- file("header.html")
writeLines('
<!-- Global site tag (gtag.js) - Google Analytics -->
<script async src=\"https://www.googletagmanager.com/gtag/js?id=G-7BMWEVFRJM\"></script>
<script>
  window.dataLayer = window.dataLayer || [];
  function gtag(){dataLayer.push(arguments);}
  gtag(\'js\', new Date());

  gtag(\'config\', \'G-7BMWEVFRJM\');
</script>
<meta name=\"description\" content=\"A live, global COVID19 numbers feed with simple analytics\">
<meta http-equiv="refresh" content="900" />
<meta http-equiv=\"Cache-Control\" content=\"no-cache, no-store, must-revalidate\" />
<meta http-equiv=\"Pragma\" content=\"no-cache\" />
<meta http-equiv=\"Expires\" content=\"0\" />
<link href="https://fonts.googleapis.com/css?family=Exo+2:300&display=swap" rel="stylesheet">
<link rel="apple-touch-icon" sizes="180x180" href="/apple-touch-icon.png">
<link rel="icon" type="image/png" sizes="32x32" href="/favicon-32x32.png">
<link rel="icon" type="image/png" sizes="16x16" href="/favicon-16x16.png">
<link rel="icon" href="/favicon.ico" type="image/x-icon" />
<link rel="shortcut icon" href="/favicon.ico" type="image/x-icon" />
<link rel="manifest" href="/site.webmanifest">
<style>
@import url(\'https://fonts.googleapis.com/css?family=Exo+2:300&display=swap\');
@import url(\'https://fonts.googleapis.com/css2?family=Roboto+Mono:wght@300&display=swap\');
</style> 
<!-- Global site tag (gtag.js) - Google Analytics -->\n <script async src="https://www.googletagmanager.com/gtag/js?id=UA-157579559-3"></script> \n <script> window.dataLayer = window.dataLayer || [];function gtag(){dataLayer.push(arguments);}gtag(\'js\', new Date()); gtag(\'config\', \'UA-157579559-3\');</script> 
<script src="https://kit.fontawesome.com/5961dcc1a3.js" crossorigin="anonymous"></script> 
<script type="text/javascript">
jQuery(function($) {
    if (/chrom(e|ium)/.test(navigator.userAgent.toLowerCase())) {
        $(\'body\').css(\'opacity\', \'1.0\') 
    }
})
</script>
<style> body {font-family: \'Exo 2\', sans-serif;font-size: 18px;}</style>
<style>
.button {
  box-shadow: 0 8px 16px 0 rgba(0,0,0,0.2), 0 6px 20px 0 rgba(0,0,0,0.19);
  background-color: #009ad0;
  border: none;
  color: white;
  padding: 8px 24px;
  text-align: center;
  font-size: 24px;
  margin: 4px 2px;
  opacity: 0.8;
  transition: 0.3s;
  display: inline-block;
  text-decoration: none;
  cursor: pointer;
  border-radius: 15px;
  opacity: .8;
  
}

.button:hover {
   opacity: 1;
   box-shadow: 0 12px 16px 0 rgba(0,0,0,0.24), 0 17px 50px 0 rgba(0,0,0,0.19);
}
</style>
', CON)
close(CON)
```
<br>
<br>
<div class = "row no-gutters">
<div class = "col-sm-8"> 
</div>
<div class = "col-sm-4" style="text-align: right">
<a href="/">
<img src="https://llvll.ch/images/llvlllogo.svg" style="width:120px; float:right;">
</a>
</div>
</div>

***

# <i class="fas fa-globe-europe"  style="color:#a0a0a0"></i> Global COVID19
<span style="color:#a0a0a0">Last Updated: `r format(Sys.time(), format='%H:%M, %B %d, %Y (%Z)')`</span>

***

## Cases: <span style="color:#009AD0">`r prettyNum(total.cases.worldometer, big.mark=",", scientific=F)`</span>
<span style="color:#a0a0a0">&nbsp;[+`r prettyNum(worldometer$NewCases[worldometer$Country.Other=="World"], big.mark=",", scientific=F)` cases today]</span> [^1]

## Recovered: <span style="color:#67d000"> `r prettyNum(total.recovered.worldometer, big.mark=",", scientific=F)`</span>

## Deaths: <span style="color:red">`r prettyNum(total.deaths.worldometer, big.mark=",", scientific=F)`</span>
<span style="color:#a0a0a0">&nbsp;[+`r prettyNum(worldometer$NewDeaths[worldometer$Country.Other=="World"], big.mark=",", scientific=F)` deaths today]</span>
<br>

 1 in `r round(1/(total.deaths.worldometer/total.cases.worldometer))` cases are fatal[^2]: `r toperson(round(1/(total.deaths.worldometer/total.cases.worldometer)),"#009AD0")` 

<br>
<span style="color:#009AD0">`r prettyNum(growth$newconfirmed[growth$Date==maxdate], big.mark=",", scientific=F)`</span> cases yesterday <br>Last 28 days: `r sparkline(tail(growth$newconfirmed,28),type="bar",barColor="#009AD0", highlightColor= 'blue',width = 150,tooltipFormatter = htmlwidgets::JS(
    sprintf(
      "function(sparkline, options, field){
  debugger;
  return %s[field[0].offset] + '<br/>' + 'Cases:' + field[0].value.toLocaleString();
}",
      jsonlite::toJSON(
        format(
          format(seq.Date(min(tail(growth$Date,28)),by="day",length.out =28), "%a %b %d")
        )
      )
    )
  )
)
`
<br><br>
<span style="color:red">`r prettyNum(growth$newdeath[growth$Date==maxdate], big.mark=",", scientific=F)`</span> deaths yesterday <br>Last 28 days:  `r sparkline(tail(growth$newdeath,28),type="bar",barColor="red", highlightColor= 'blue' ,width = 150, tooltipFormatter = htmlwidgets::JS(
    sprintf(
      "function(sparkline, options, field){
  debugger;
  return %s[field[0].offset] + '<br/>' + 'Deaths:' + field[0].value;
}",
      jsonlite::toJSON(
        format(
          format(seq.Date(min(tail(growth$Date,28)),by="day",length.out =28), "%a %b %d")
        )
      )
    )
  )
)
`
<br><br><br><br>

***
[^1]: Number in square brackets: reported since midnight today (GMT+0)
[^2]: For multiple reasons, the number of deaths divided by the number of cases is not the mortality rate of COVID19. It is the percentage of individuals identified to have COVID19 who are now dead.. 

# Number of deaths per day {#gdpd}


<br>

```{r  echo=FALSE, message=FALSE, warning=FALSE, out.width="100%",fig.height=4 }
library(zoo)
growth<-growth %>% arrange(Date) %>%
       mutate(ma2=rollapply(newdeath,7,mean,align='right',fill=NA))

if(!file.exists("growthtime.html") | as.numeric(Sys.Date()-(as.Date(file.info("growthtime.html")$mtime-6*60*60)))>0) { 

fig <- plot_ly(hoverinfo = "text", text = paste(format(growth$Date, "%a %b %d"),"<br>Deaths:",prettyNum(growth$newdeath, big.mark=",", scientific=F),sep=""),type = 'scatter', mode = 'lines')
fig <- fig %>% add_trace( x = ~growth$Date,
                          y = ~growth$ma2, 
                          fill = 'tozeroy',
                          fillcolor = 'rgba(00,9a,d0,.5)',
                          line = list(
                               color = '#009ad0'
                          )
               )
fig <- fig %>% layout(
    title = "",
    xaxis = list(
      title = "Date",
      rangeselector = list(
        buttons = list(
           list(
            count = 7,
            label = "1 wk",
            step = "day",
            stepmode = "backward"),
           list(count = 1,
            label = "1 mo",
            step = "month",
            stepmode = "backward"),
           list(step = "all"))),

 #     rangeslider = list(type = "date",title = "Date")),
            rangeslider=list(
            visible=FALSE
        )),    

   yaxis = list(title = "Daily Deaths (7 day rolling average)"))
fig<- fig %>% config(displayModeBar = FALSE)
fig <- fig %>% layout(showlegend = FALSE)
saveWidget(fig, "growthtime.html", selfcontained = F, libdir = "lib")
}

htmltools::tags$iframe(
  src = "growthtime.html", 
  width="100%",
  height=400,
  scrolling = "no", 
  seamless = "seamless",
  frameBorder = "0"
)
```


```{r  eval=FALSE,echo=FALSE, message=FALSE, warning=FALSE , out.width="100%",fig.width=10, fig.height=7, cache=FALSE}
#((as.numeric(Sys.Date()-(as.Date(file.info(thefile1)$mtime-6*60*60))>0 | (!file.exists(thefile1))))){
# 
# #Make sure that all countries in the last frame are also in the first frame
# 
id="Italy"
  onsetdaydeathplot<-onsetdaydeath[onsetdaydeath$Country.Region!="China",]

doublingbreaks$new.in.last10<-100*(1-2^(-10/doublingbreaks$days))
notationdf<-data.frame(value="GOAL: ZERO GROWTH",title=paste("Data up to:",max(df$Date)))

gg<-ggplot(onsetdaydeathplot) +
#  geom_segment(data=doublingbreaks,aes(x = 5, y = new.in.last10, xend =1.2*max(onsetdaydeathplot$day.since.onset.10death), yend = new.in.last10),colour="#009AD0",alpha=.4,linetype = "dashed") + 
#  geom_text(data=doublingbreaks,aes(0.5,new.in.last10+1.5,  label=paste("double in",doublingbreaks$days,"days")),size=3,colour="#009AD0",hjust=0) + 
  geom_abline(aes(slope=0, intercept=0),colour="#67D000",size=2, alpha=1,linetype = "dashed") + 
  geom_text(data=notationdf,aes(0.5,3,label = value), size=4,colour="#67D000", alpha=1,hjust=0)+
  geom_line(data=onsetdaydeathplot %>% filter(day.since.onset>=0,Country.Region==id), 
                aes(day.since.onset.10death, 
                new.deaths.in.last.7.days,
                colour=continent.y,
                group=Country.Region), alpha=.8, size=1,
                show.legend=FALSE)+
  geom_point(data=onsetdaydeathplot %>% group_by(Country.Region) %>% filter(Date == max(Date)), 
             aes(day.since.onset.10death,
                 new.deaths.in.last.7.days,
                 size=.5+number.death/200,
                 colour=continent.y,
                show.legend=FALSE),                 
                alpha=.1)+
  
  geom_point(data=onsetdaydeathplot %>% group_by(Country.Region) %>% filter(Date == max(Date),Country.Region==id), 
             aes(day.since.onset.10death,
                 new.deaths.in.last.7.days,
                 size=.5+number.death/200,
                 colour=continent.y,
                show.legend=FALSE),                 
                alpha=.6)+
geom_text_repel(data=onsetdaydeathplot %>% group_by(Country.Region) %>% filter(Date == max(Date), day.since.onset.10death>35,new.deaths.in.last.7.days>30,Country.Region!=id),
                    aes(day.since.onset.10death,
                        new.deaths.in.last.7.days,
                        label=Country.Region),force=10,nudge_x=3,  alpha=.3, segment.color = "grey90") +
  geom_text_repel(data=onsetdaydeathplot %>% group_by(Country.Region) %>% filter(Date == max(Date),Country.Region==id) ,
                  aes(day.since.onset.10death,
                      new.deaths.in.last.7.days,
                      label=Country.Region),force=10,nudge_x=10,  segment.color = "grey90") +
  scale_x_continuous("days since 10 deaths",limits=c(0,1.2*max(onsetdaydeathplot$day.since.onset.10death)),breaks = seq(0, 1.2*max(onsetdaydeathplot$day.since.onset.10death), by = 14))  +
  scale_y_continuous("% deaths occuring in last 7 days", limits=c(0,100), breaks=c(0,25,50,75,100),labels=c("  0%","   25%","   50%","   75%","  100%"))  +
  scale_size(name="",range = c(.5, 45),breaks=c(.5,125),labels=c("10 deaths",paste(as.character(prettyNum(max(onsetdaydeathplot$number.death),big.mark=",", scientific=F)),"deaths")))+
  ggtitle(notationdf$title)+
  theme_ipsum() + 
  theme(panel.grid.minor=element_blank())
gg<-gg + theme(legend.position = "top")+ theme(plot.title = element_text(color="lightgrey", size=14))+ scale_color_jcolors(name="size = total deaths",palette = "pal3")
gg+guides(color = guide_legend(order=1),
         size = FALSE,
         shape = FALSE)+ theme(legend.background = element_rect(fill="#ffffff",
                                  size=0.5, linetype="solid", 
                                  colour ="#efefef"))


```

```{r eval=FALSE,echo=FALSE, message=FALSE, warning=FALSE, out.width="100%",fig.width=10,fig.height=3, cache=FALSE}
if(TRUE){
#if((as.numeric(Sys.Date()-(as.Date(file.info(thefile2)$mtime-6*60*60))>0 | (!file.exists(thefile2))))){
ymaxrange<-onsetdaydeathplot %>%
           filter(Country.Region==id)
ymaxrangeupper<-max(ymaxrange$new.deaths.in.last.7.days*ymaxrange$number.death/100)


gg<-ggplot(onsetdaydeathplot)+
  geom_line(aes(day.since.onset.10death,
                  new.deaths.in.last.7.days*number.death/100,
                group=Country.Region,
                colour=continent.y),
                alpha=.1,
                show.legend=FALSE)+
    geom_point(data=onsetdaydeathplot %>% group_by(Country.Region) %>% filter(Date == max(Date)) %>% ungroup() , 
             aes(day.since.onset.10death,
                  new.deaths.in.last.7.days*number.death/100,
                 group=Country.Region,
                 colour=continent.y),
                 alpha=.1,
             size=.5,
                show.legend=FALSE)+
      geom_point(data=onsetdaydeathplot %>% group_by(Country.Region) %>% filter(Country.Region==id,Date == max(Date)) %>% ungroup() , 
             aes(day.since.onset.10death,
                  new.deaths.in.last.7.days*number.death/100,
                 group=Country.Region,
                 colour=continent.y),
                 alpha=.8,size=3,shape=3,
                show.legend=FALSE)+
    geom_line(data=ymaxrange,
              aes(day.since.onset.10death,
                  new.deaths.in.last.7.days*number.death/100,
                group=Country.Region,
                colour=continent.y),
                alpha=.8, size=1,
                show.legend=FALSE)+
    geom_text_repel(data=onsetdaydeathplot %>% filter(Country.Region==id,Date == max(Date)) ,
                  aes(day.since.onset.10death,
                  new.deaths.in.last.7.days*number.death/100,
                      label=Country.Region),
                  force=10,
                  nudge_x=10,  
                  segment.color = "grey90") +
    geom_text_repel(data=onsetdaydeathplot %>% filter(Country.Region!=id,Date == max(Date),(new.deaths.in.last.7.days*number.death/100>(ymaxrangeupper/2)) | day.since.onset.10death>-1+max(onsetdaydeathplot$day.since.onset.10death[onsetdaydeathplot$Country.Region==id]))   ,
                  aes(day.since.onset.10death,
                new.deaths.in.last.7.days/100*number.death,
                      label=Country.Region),
                  force=10,
                  nudge_x=1,  
                  segment.color = "grey90",
                  alpha=.2) +
  scale_y_continuous("total deaths in last 7 days", label=comma)+
  scale_x_continuous("days since 10 deaths",limits=c(0,1.2*max(onsetdaydeathplot$day.since.onset.10death)),breaks = seq(0, 1.2*max(onsetdaydeathplot$day.since.onset.10death, na.rm = T), by = 14))  +
  theme_ipsum()+ scale_color_jcolors(palette = "pal3")+ 
  theme(panel.grid.minor=element_blank())
gg + theme(legend.position = "none")+ theme(plot.title = element_text(color="lightgrey", size=14))+ scale_color_jcolors(palette = "pal3")
} else{
   knitr::include_graphics(thefile2)
}

```

# Select a Country

Click <i class="fas fa-mouse-pointer" style="color:#009AD0"></i> on a country name in the table below to go to that country's summary page.

Data for all countries with COVID19 cases are also accessible using the search box above the table. Searches can be performed via [regex](https://regex101.com/). This means that if you want to see the numbers for Italy, France and Germany only: type **Italy|Germany|France** into the search box.
<br>

```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="100%",fig.height=8 }

datatable(df.table ,
          colnames = c("<i class=\"fas fa-globe-americas \"></i>",
                       "<i class=\"fas fa-procedures \" title=\"Total confirmed COVID19 cases\" > </i> Cases",
                       "<i class=\"fas fa-book-dead \" title=\"Total COVID19 fatalities\"> </i> Deaths",
                       "<i class=\"fas fa-book-dead \" title=\"Percent of identified COVID19 cases that prove fatal\">&nbsp</i><i class=\"fas fa-percent\"></i>",
                       "<i class=\"fas fa-vial\" title=\"Tests\"></i> Tests",
                       "<i class=\"fas fa-vial\" title=\"Tests\"></i> per 1M <i class=\"fas fa-male\" title=\"people in country\">",
                       "<i class=\"fas fa-male\" title=\"people in country\">  </i> Population"),
          options = list( order = list(list(2,'desc')),
                          search = list(regex = TRUE, caseInsensitive = TRUE),
                          columnDefs = list(list(className = 'dt-right', targets = 1:6)
                                            
      )
                        ),
          rownames = FALSE,
          escape=F,
          autoHideNavigation =T)



```

***

<center>
<button class="button"  onclick="location.href='http://llvll.ch/indexfull.html'" ><span> <i class="fas fa-globe-americas"> </i> <i class="fas fa-mouse-pointer"></i>  click for analysis</span></button>
</center>
<br>



## <i class="fas fa-book"  style="color:#888888"></i> Other Resources:
- WHO [rolling updates](https://www.who.int/emergencies/diseases/novel-coronavirus-2019/events-as-they-happen)
- [NEJM COVID19](https://www.nejm.org/coronavirus?query=RP) article repository
- [lesswrong.com](https://www.lesswrong.com/coronavirus-link-database) link database

## <i class="fas fa-database"  style="color:#888888"></i> Data Sources: 
- COVID19 Historical: [Johns Hopkins CSSE](https://github.com/CSSEGISandData/COVID-19/blob/master/README.md)
- COVID19 Live: [Worldometers](https://www.worldometers.info/coronavirus/)
- Population: [World Bank](`r url`)

***
